Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
cut abstract

\begin{abstract}
%
This work presents a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are described as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals that are manipulated by the controller block.  The
approach works in two stages, leveraging the use of counter-example guided
inductive synthesis (CEGIS) and reachability analysis.  The former
synthesises a static feedback controller that stabilizes the system under
some restrictions given by the safety of the reach space.  The latter
verifies its potential safety by means of either of the following
approaches: forward reachability analysis via unfolding of the dynamics or
invariant set generation via abstract acceleration; if the verification step
fails, we loop back to seek an alternative controller benefiting from the
obtained counterexamples to safety using solution generalization and
abstraction refinement.  We are able to efficiently synthesize stable and
safe controllers considering a set of intricate physical plant models taken
from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

>>>>

\begin{abstract}
%
This work presents a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are described as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals by the controller.  The approach works in two
stages, leveraging counterexample guided inductive synthesis (CEGIS) and
reachability analysis.  CEGIS synthesises a static feedback controller that
stabilizes the system under some restrictions given by the safety of the
reach space.  Safety is verfied iether via BMC or abstract acceleration; if
the verification step fails, we generate an alternative controller by
generalizing the counterexample.  We synthesize stable and safe controllers
for intricate physical plant models from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}
